---
title: "Analysis of War - the card game"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduciton

Have you ever played War? have you ever wondered __When will this be over!?__

Well I have, and after a weekend of being forced to play with my little cousin, I decided enough is enough. Lets do some simulation and some data analysis to answer some basic questions:

* How long does the average game take
* How does the initial hand affect your winning percentage?
    * How often will I win if I have all the aces?
    * How often will I win depending on the average hand strength?
* How does the anti size affect game duration?

## Rules

# Simulation in python
## Setup

Since I am not too used to dealing with numerical simulations of card games, I'm going to set up some classes in python. Once the simulations are done I'll import the data into R to do some analysis. 

Here are the two classes I set up:
```{r cache=FALSE, echo=FALSE}
knitr::read_chunk('game.py')
knitr::read_chunk('generate.py')
```


```{python classes, eval=FALSE}
```
## Simulation

Now lets run the simulations:

```{python, sim, eval=FALSE}
```
# Running the analysis in R
## Setup

First lets load up packages and set up the data from python

```{r load_lib, message=FALSE}
library(dplyr)
library(ggplot2)
```

```{r load_data}
results_paths = list.files('../output', 'results_[0-9]+.csv', full.names = T)
results = do.call(rbind, lapply(results_paths, read.csv))

colnames(results) = c('war_anti', 'winner', 'num_turns','player0_mean', paste0("player0_", c(as.character(2:10), 'J', 'Q', 'K', 'A'),'s'))
```
## Analysis

Lets take a look at the data:

```{r}
head(results)
```
Now lets plot the data

```{r plot}
results %>% ggplot(aes(x =factor(winner), y=player0_mean)) + geom_boxplot() + facet_wrap(~war_anti)
```

